---
title: "Amigos_Assignment4"
author: "Pranali Angne"
author: "Nishtha Arora"
author: "Raunak Bhivpathaki"
date: "5/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\section*{1}
```{r}
library(tidyverse)
library(lubridate)
```



```{r Reading-data}
question0 <-read_csv("data/building-approvals.csv")

summary <- colnames(question0)

knitr::kable(summary, col.names = gsub("[.]", " ", names(summary)), align = "c")
```



Above are the description of the variables used in the dataset.
+ *Date of decision notice*: The date the building certifier made a notice that the works met the building codes.

+ *Decision*: Current status of the works as recorded with Council.

+ *Class*: The building classification as per the list on page one.

+ *Sub-category (Council category descriptors)*: This category is a subdivision of class. Provides information regarding additions, alterations, subdwell etc in it.

+ *Category*: Townsville City Council has published on its website for a number of years a summary of building approval data using the certain categories.

+ *Estimated values*: The monetary value of the proposed building work.

+ *Suburb*: The suburb where the building work is taking place.

+ *Floor area*: The floor area of the building works in square metres.

+ *No. of units*: Number of individual units created or demolished by the building works.

+ *Electoral Division*: The local government electoral division in which the works are occurring.


# Q1: Which **Year** has maximum approvals regarding the building category which is maximum in demand/most favourite.

```{r }
question1 <- question0 %>% 
  mutate(`Date Of Decision Notice` = dmy(`Date Of Decision Notice`),
        Year = year(`Date Of Decision Notice`)) %>% 
  select(Year, Decision) %>% 
  count(Decision, Year) %>% 
  rename(`Total number of Decision` = n)

# plotting this graph
ggplot(data = question1, aes(x = Year,
                             y = `Total number of Decision`, 
                             fill = Decision)) +
  geom_bar(stat="identity", position = "dodge") +
  scale_fill_brewer(palette="Dark2") +
  theme_get() +
  xlab("Year") +
  ylab("Total count of Decision") 
```


\section*{2}


\section*{3}